%-------------------------------------
% Resum in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

\documentclass[a4paper, 10pt]{article}
\usepackage{myresume}  % Style package

% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  \item {\Calluna \faPhone~(+852) 5394-5058}  % 使用 FontAwesome 图标
  \item {\Calluna \faEnvelope~ychenlg@connect.ust.hk.com}
  \item {\Calluna \faGlobe~\href{https://517adam.github.io/}{517adam.github.io}}
\end{flushright}\vspace{-40pt}

\begin{flushleft}
  {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{Yuanzhong Chen}} \hfill
  {\Calluna \fontsize{14.5pt}{14.5pt}\selectfont \textsc{B.Sc.}}
  \noindent\rule{\textwidth}{0.6pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\eduHeading
  {Dept. of Computer Science \& Mathematics, HKUST}{Hong Kong, China}
  {B.Sc. in Computer Science and Mathematics}{2023 -- 2027 \footnotesize{\textit{(expected)}}}
\itemListStart
  \myItem{Research: Machine Learning, Deep Learning, Computational Pathology}
\itemListEnd

\eduHeading
  {Stanford University}{California, USA}
  {International Honors Program}{2025.6 -- 2025.8}
}

% -------------------- RESEARCH --------------------
\sectionBlock{
\section{Research}
}{
\pubListStart
{\textbf{Multimodal Learning for Cancer Diagnosis and Prognosis} \\
Supervised by Prof. Hao Chen}
{Computational pathology research for cancer diagnosis using Whole Slide Images}{2024.9 -- 2025.9}
\pubListEnd
}

% -------------------- PROJECTS --------------------
\sectionBlock{
\section{Projects}
}{
\projHeading
{\textbf{Zero-Shot Spatial Reasoning with LLMs}}
{Course Project, COMP5214}{2025.3 -- 2025.5}
\itemListStart
  \myItem{Explored spatial reasoning capabilities of large language models in zero-shot settings.}
\itemListEnd

\projHeading
{\textbf{Survey on Cancer Diagnosis with WSI Images}}
{Undergraduate Research Opportunity Program}{2024.9 -- 2025.9}
\itemListStart
  \myItem{Reviewed state-of-the-art methods for cancer diagnosis using whole slide imaging.}
\itemListEnd
}

% -------------------- INTERNSHIPS --------------------
\sectionBlock{
\section{Internships}
}{
\internHeading
  {iFLYTEK Ltd.}{Hefei, China}{2024.06 -- 2024.08}
\itemListStart
  \myItem{Developed scripts for web data collection and preprocessing for unsupervised learning.}
  \myItem{Prepared reports and summarized research findings.}
\itemListEnd
}

% -------------------- AWARDS & HONORS --------------------
\sectionBlock{
\section{Awards \& Honors}
}{
\awardListStart
\item \emph{Dean's List}, HKUST \hfill 2023.9--2025.6 (4 times)
\item \emph{The Continuous Scholarship (Top 2\% students)}, HKUST \hfill 2023--2024
\awardListEnd
}

% -------------------- SKILLS --------------------
\sectionBlock{
\section{Skills}
}{
\skillListStart
\item \emph{Languages}: Mandarin (Native), English
\item \emph{Programming}: Python, C++, MATLAB, R, CSS, HTML, PyTorch, TensorFlow
\skillListEnd
}

% -------------------- COURSES --------------------
\sectionBlock{
\section{Selected Courses}
}{
\CourseListStart
\item \emph{MAHT2431 Honors Probability}
\item \emph{COMP5214 Advanced Deep Learning Architecture}
\item \emph{CS229 Machine Learning (Stanford)}
\CourseListEnd
}
\end{document}